
<ul class="navibar">
  <li><a href="./index.html" class="current" >Schedule</a></li>
  <li><a href="./syllabus.html" class="navibar" >Syllabus</a></li>
  <li><a href="./homework.html" class="navibar" >Homework</a></li>
</ul>




<!--- Start Main Page --->
<br><br>

### Schedule

-----------


```{r, include=FALSE, cache=FALSE, echo=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(knitr)
source("make_calendar.R")
source("schedule.R")
```


```{r, echo=FALSE}

left_join(calendar, schedule,by="Class") %>% 
  replace_na(list(Topic.x='', Topic.y='', Reading='', Notes='')) %>% 
  unite('Topic', Topic.x, Topic.y, sep='') %>% 
  rename(`Reading (Pre-Class)` = Reading) %>% 
  knitr::kable(format="pandoc")
```


-------------------------------------------------------

#### Reading 

- ISL: [**An Introduction to Statistical Learning** by James, Witten, Hastie and Tibshirani](http://www-bcf.usc.edu/~gareth/ISL/)
- ESL: [**The Elements of Statistical Learning: Data Mining, Inference, and Prediction (2nd Edition)** by Hastie, Tibshirani, and Friedman](http://www-stat.stanford.edu/~tibs/ElemStatLearn/)]
- ITDM: [**Introduction to Data Mining (Second Edition)** by Tan, Steinbach, Karpatne, and Kumar](https://www-users.cs.umn.edu/~kumar001/dmbook/index.php)
- MMDS: [**Mining of Massive Datasets** by Jure Leskovec, Anand Rajaraman, Jeff Ullman](http://www.mmds.org/)
