---
title: "Homework #0: Hello SYS-6018" 
author: "**Your Name Here**"
date: "Due: Tue Jan 31 | 11:45am (ungraded)"
output: R6018::homework
---

**SYS 4582/6018 | Spring 2023 | University of Virginia **

*******************************************
```{r config, echo=FALSE}
source(system.file("config/hw_config.R", package="R6018")) # knitr settings
# options(dplyr.summarise.inform = FALSE)  # ignore dplyr message about grouping
```


# Required R packages and Directories

::: {.solution}

```{r packages, message=FALSE, warning=FALSE}
data.dir = 'https://mdporter.github.io/SYS6018/data/' # data directory
library(R6018)     # functions for SYS-6018
library(tidyverse) # functions for data manipulation    
```

:::

# Getting Help

The purpose of this (ungraded) homework is to help get you prepared for the semester. Don't panic if you don't immediately know the answers to some of these. I expect everyone will need to look things up. Take note of the areas that are rusty and plan to spend a bit of extra time to get up to speed. If some of these items are not even remotely familiar to you, then you probably have not satisfied the pre-requisite material; review the course syllabus and speak to me about any questions.

The teaching staff (TA and myself) are here to help! Don't wait too long before asking for help and do let us know right away if you are starting to fall behind. I will also publish the solutions right after due date. It is **highly encouraged** that you study the posted solutions.

Use the class Teams channel to ask questions. 

# R Resources

## a. Update R and RStudio

- Use the latest version (R > `r with(R.version, str_c(major, ".", minor))`, RStudio > `r rstudioapi::versionInfo()$version`)

-   Help with installation <https://rladiessydney.org/courses/ryouwithme/01-basicbasics-1/> and <https://moderndive.netlify.app/1-getting-started.html> and <https://education.rstudio.com/learn/beginner/>


## b. Install/Update the following packages we will meet during this course:

-   Working with Data: `tidyverse`
-   Utility: `remotes`
-   Data: `ISLR`, `moderndive`, `MASS`
-   Resampling: `boot`, `rsample`
-   Modeling: `tidymodels`, `modelr`, `broom`
-   Regression: `glmnet`, `FNN`, 
-   Classification: `e1071`, 
-   Trees: `rpart`, `rpart.plot`, `randomForest`, `ranger`
-   Ensembles: `gbm`, `xgboost`
-   Density Estimation: `fitdistrplus`, `ks`
-   Clustering: `mclust`, `mixtools`
-   Association Analysis: `arules`
-   Networks: `igraph`

Note: Do not call `install.packages()` in this RMarkdown document; it only needs to be done once from the console. However you will need to use `library()` in RMarkdown since it needs to be called every time the Rmarkdown is compiled.


## c. Install the course R package `R6018`

The `R6018` package contains formatting for the homework and some helpful functions. This R package is not hosted on CRAN, but on github. You can install it with this command `remotes::install_github("mdporter/R6018")` on your console (make sure you have installed the `remotes` package first!). This RMarkdown file won't compile until you do this. 


# Tidyverse Resources

Read the following sections in [R for Data Science](https://r4ds.had.co.nz):

## Explore
- [3 Data visualisation](https://r4ds.had.co.nz/data-visualisation.html)
- [4 Workflow: basics](https://r4ds.had.co.nz/workflow-basics.html)
- [5 Data transformation](https://r4ds.had.co.nz/transform.html)
- [6 Workflow: scripts](https://r4ds.had.co.nz/workflow-scripts.html)
- [7 Exploratory Data Analysis](https://r4ds.had.co.nz/exploratory-data-analysis.html)
- [8 Workflow: projects](https://r4ds.had.co.nz/workflow-projects.html)

## Wrangle
- [10 Tibbles](https://r4ds.had.co.nz/tibbles.html)
- 11 Import
    - [11.2](https://r4ds.had.co.nz/data-import.html#getting-started)
- 12 Tidy data
    - [12.3 Pivoting](https://r4ds.had.co.nz/tidy-data.html#pivoting)
    - [12.5 Missing Values](https://r4ds.had.co.nz/tidy-data.html#missing-values-3)
- [15 Factors](https://r4ds.had.co.nz/factors.html)

## Program
- [17 Introduction](https://r4ds.had.co.nz/program-intro.html)
- [18 Pipes](https://r4ds.had.co.nz/pipes.html)
- [19 Functions](https://r4ds.had.co.nz/functions.html)
- [20 Vectors](https://r4ds.had.co.nz/vectors.html)
    -  20.1-20.4
- [21 Iteration](https://r4ds.had.co.nz/iteration.html)
    - 21.1 - 21.5

## Model
- 23 Model basics
    - [23.4 Formulas](https://r4ds.had.co.nz/model-basics.html#formulas-and-model-families)


## Communicate
- [27 R Markdown]((https://r4ds.had.co.nz/r-markdown.html))
- [28 Graphics for communication](https://r4ds.had.co.nz/graphics-for-communication.html)
    - *optional*
- [29 R Markdown formats](https://r4ds.had.co.nz/r-markdown-formats.html)
    - *optional*

# Save/Bookmark the following cheatsheets and resources

## **RStudio and RMarkdown**

-   [RStudio IDE Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/rstudio-ide.pdf)

-   [R Markdown Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/rmarkdown.pdf)

-   [R Markdown Reference Guide](https://github.com/rstudio/cheatsheets/raw/main/rmarkdown-2.0.pdf)

-   [Latex Cheatsheet](https://wch.github.io/latexsheet/latexsheet-0.png)

## **R**

- [Base R](https://github.com/rstudio/cheatsheets/blob/main/base-r.pdf)

- [Data Visualization Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/data-visualization.pdf)
    - [`ggplot2` website](https://ggplot2.tidyverse.org/)

- [Data Transformation Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/data-transformation.pdf)
    - [`dplyr` website](https://dplyr.tidyverse.org/)
    - [`tidyr` website](https://tidyr.tidyverse.org/)

- [Factors with forcats Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/factors.pdf)
    -   [`forcats` website](https://forcats.tidyverse.org/)

- [Data Import Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/data-import.pdf)
    - [`readr` website](https://readr.tidyverse.org/)
    - [`tidyr` website](https://tidyr.tidyverse.org/)

- [Apply Functions Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/purrr.pdf)

    - [`purrr` website](https://purrr.tidyverse.org/)

## **Python with RStudio/RMarkdown** (Optional)

- [Python with R and Reticulate    Cheatsheet](https://github.com/rstudio/cheatsheets/raw/main/reticulate.pdf)



# Problem 1: Math Notation

## a. What are the equations for the least squares coefficients in linear regression (in matrix notation)? Use $X$ for the design/predictor matrix, and $Y$ the vector of responses.

::: {.solution}
Solution here
:::

## b. Let $x_1, x_2, \ldots, x_n$ be a sample of length of time that a customer is on the phone with a call center help line. We feel comfortable modeling the data as coming from an *exponential distribution*. What is the MLE (Maximum Likelihood Estimate) of the parameter? Show your steps.

::: {.solution}
Solution here
:::


# Problem 2: Coding Practice

## a. Simulate 100 observations from the following model:

-   $X \sim N(1, 1)$
-   $Y \sim N(1 + 2X, 2)$
-   $Z = \begin{cases} 1 &\quad Y<0 \\ 2 &\quad Y \ge 0 \end{cases}$

::: {.solution}
Solution here
:::

## b. Make a scatter plot of the data. Put $X$ on the x-axis and $Y$ on the y-axis. Color the points according to $Z$.

::: {.solution}
Solution here
:::

## c. Write a function that adds two numbers together and squares the result.

::: {.solution}
Solution here
:::

## d. Write a loop to calculate the mean of every column in `mtcars`. 

::: {.solution}
Solution here
:::

# Problem 3: Statistics

## a. Find the two [quantiles](https://en.wikipedia.org/wiki/Quantile) that capture 95% of the following data:

```{r}
set.seed(2023)
x = runif(n=100, min=2, max=22)
```

::: {.solution}
Solution here
:::

## b. Confidence Interval

A new machine learning model, developed by UVA researchers, uses biopsy images to predict if a child has enteropathy or celiac disease. [In a study of 102 patients](https://jamanetwork.com/journals/jamanetworkopen/fullarticle/2735765), the model was able to correctly classify 95 of the images.

Find the 90% [confidence interval](https://en.wikipedia.org/wiki/Confidence_interval) for the probability a patient is correctly classified?

::: {.solution}
Solution here
:::

## c. Linear Models

-   Albemarle County real estate assessment data can be found here <https://raw.githubusercontent.com/uvastatlab/phdplus2021/main/data/albemarle_real_estate.csv>.

-   Fit a linear regression model that predicts the `TotalValue` using the predictors: `Condition`, size (`FinSqFt`), and location (`City`).

-   What are the estimated coefficients?

-   What is the estimated `TotalValue` for home with the following characteristics?

```{r, echo=FALSE}
tibble(FinSqFt = c(2500, 1850),
       City = c('EARLYSVILLE', 'CROZET'),
       Condition = c('Good', 'Fair'))
```

::: {.solution}
Solution here
:::

## d. Hypothesis Testing 

Use the `movies_sample` (IMDb) data from the `moderndive` R package to performance a hypothesis test that *Action* movies are ranked lower (on average) than *Romance* movies.

::: {.solution}
Solution here
:::









