---
title: "Homework #0"
author: "**Your Name Here**"
date: "Due: Thu Aug 27 1:55pm"
output: 
  html_document:
  #html_notebook:  
    df_print: kable
---

**SYS 6018 | Fall 2020 | University of Virginia **

*******************************************

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5,     # set figure width
                      fig.align = "center",# set figure position
                      out.width = "49%", # set width of displayed images
                      warning=FALSE,     # do not show R warnings
                      message=FALSE)     # do not show R messages
options(dplyr.summarise.inform = FALSE)  # ignore message about group structure

```

<!--- Solution Region --->
```{css solution-region, echo=FALSE}
.solution {
  background-color: #232D4B10;
  border-style: solid;
  border-color: #232D4B;
  padding: .5em;
  margin: 20px
}
```

<!--- Load Required R packages here --->
```{r, include=FALSE}
#- Better table printing
library(kableExtra) # https://haozhu233.github.io/kableExtra/awesome_table_in_html.html
format_table <- function(x, nmax=10) {
  kable(x) %>% 
    kable_styling(full_width = FALSE, font_size=11, position = "left") %>% 
    {if(nrow(x) > nmax) scroll_box(., width = "100%", height = "200px") else .}
}
#- useful functions
digits <- function(x, k=2) format(round(x, k), nsmall=k)
#- data directory
data.dir = 'https://mdporter.github.io/SYS6018/data/'
#- required functions
library(tidyverse)
```

### Problem 0.1: Who are you?

a. What is your name? 

<div class="solution">
Solution Here
</div>

b. Where are you from (e.g., hometown)? 

<div class="solution">
Solution Here
</div>

c. What do you hope to do after graduation (be specific)?  

<div class="solution">
Solution Here
</div>

d. List 3 interesting things about yourself. 

<div class="solution">
Solution Here: Look up how to make a enumerated list in markdown! 
</div>


----------

### Problem 0.2: About the course

a. What are you most excited to learn in this course?

<div class="solution">
Solution Here
</div>


b. What pre-req topics (e.g., math, coding, probability, statistics) are your weakest? 

<div class="solution">
Solution Here
</div>


c. What pre-req topics are your strongest? 

<div class="solution">
Solution Here
</div>

d. Would you rather see the mathematical details or coding details of a method/algorithm? 

<div class="solution">
Solution Here
</div>

----------

### Problem 0.3: Math Notation

a. What are the equations for the least squares coefficients in linear regression (in matrix notation)? Use $X$ for the design/predictor matrix, and $Y$ the vector of responses. 

<div class="solution">
Hello LaTex! (<https://www.latex-tutorial.com/tutorials/amsmath/>, <https://www.overleaf.com/learn/latex/Mathematical_expressions>)
</div>


b. Let $x_1, x_2, \ldots, x_n$ be a sample of length of time that a customer is on the phone with a call center help line. We feel comfortable modeling the data as coming from an *exponential distribution*. What is the MLE (Maximum Likelihood Estimate) of the parameter?  Show your steps.

<div class="solution">
*Don't panic, breath, remember this is not for credit!*
</div>

---------

### Problem 0.4: Coding

a. Simulate 100 observations from the following model:

- $X \sim N(1, 1)$
- $Y \sim N(1 + 2X, 2)$
- $Z = \begin{cases} 1 &\quad Y<0 \\ 2 &\quad Y \ge 0 \end{cases}$

<div class="solution">
Let R shine - avoid loops by using vector operations. 
</div>


b. Make a scatter plot of the data. Put $X$ on the x-axis and $Y$ on the y-axis. Color the points according to $Z$. 

<div class="solution">
Can you use ggplot2?
</div>








