---
title: "Homework #2"
author: "**Your Name Here**"
date: "Due: Mon Feb 04 9:30am"
output: html_document
---

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5,     # set figure width
                      out.width = "50%", # set width of displayed images
                      warning=FALSE,     # do not show R warnings
                      message=FALSE)     # do not show R messages
```

<!--- Solution Region --->
<style>
#solution {
  background-color: #8FBC8F;
  border-style: solid;
  border-color: blue;
  padding: .5em;
  margin: 20px
}
</style>



**SYS 4582/6018 | Spring 2019 | University of Virginia **

*******************************************

<!--- Load Required R packages here --->
```{r, include=FALSE}
library(tidyverse)
library(igraph)
digits <- function(x, k=2) format(round(x, k), nsmall=k)
```


### Problem 2.1 The Marvel Universe

[Alberich, Miro-Julia, \& Rossell&oacute; (2002)](https://arxiv.org/pdf/cond-mat/0202174.pdf) 
examined the social network structure of the Marvel Comics Universe and found some similarities to real-world collaboration networks. 
The folks at <http://syntagmatic.github.io/exposedata/marvel/> have made the network data available (along with some nice visualizations). I have extracted the Hero Social Network Data which can be accessed using [this link](https://raw.githubusercontent.com/mdporter/SYS6018/master/data/marvel_hero-network.csv). Note that the data contain one edge for each time a hero appeared in the same comic, so there will be multiple edges. 


a. Load the data and make a *weighted* and *undirected* graph, where the `weight` corresponds to the number of times the heros appeared in the same comic. Ensure your graph has an edge attribute named `weight`. The weight between *LITTLE, ABNER* and *BLACK PANTHER/T'CHAL LITTLE* should be $7$. 


<div id="solution">
Solution Here
</div>



b. Run the *fast-greedy* community detection algorithm (`igraph::cluster_fast_greedy()`). How many communities did it find? Show a barplot/histogram of the community sizes (i.e., how many nodes are in each community). 

<div id="solution">
Solution Here
</div>



c. Calculate the following centrality scores for the network: *eigenvector, betweeness, and degree*. Show the top 10 heros arranged by *eigenvector centrality*. Which hero has the largest eigenvector centrality? How does this make the hero *important*? 

<div id="solution">
Solution Here
</div>

d. Show the 3 centrality scores, sorted by *betweeness centrality*, for the three largest communities. How are these three heros *important*.

<div id="solution">
Solution Here
</div>

       





### Problem 2.2: Alpha Centrality

<!---
Eigenvector-like measures of centrality for asymmetric relations
Phillip Bonacich, Paulette Lloyd
Social Networks 23 (2001) 191–201
--->

[Bonacich and Lloyd (2001)](https://github.com/mdporter/SYS6018/raw/master/other/alpha-centrality_Bonacich.pdf) introduced *alpha centrality* as an alternative to eigenvector centrality. Their main idea is that the importance of a node is based on the network structure **plus** some known external sources of importance. The alpha centrality vector $x$ is defined:
\[ 
x = \alpha  A^T x + s
\]
where $s$ is the vector of exogenous importance and $0 \leq \alpha \leq 1/\lambda_1$ (where $\lambda_1$ is the maximum eigenvalue of $A$) reflects the relative importance of the endogenous factors of importance.


a. PageRank can be considered a special case of alpha centrality. What does PageRank use for $s$, $\alpha$, and $A$? Use the notation from the class notes,  e.g., $\alpha=d$. 

<div id="solution">
Solution Here
</div>

---

<div style="background-color:lightgrey; display: block; border-color: black; padding:1em">

The next few problems will explore how alpha centrality can be used for identifying the bad actors in the money laundering data. The money laundering data was used in class and can be accessed here:

- nodes: <https://raw.githubusercontent.com/mdporter/SYS6018/master/data/transfers_nodes.csv>

- edges: <https://raw.githubusercontent.com/mdporter/SYS6018/master/data/transfers.csv>

</div>


b. Make one *directed* and one *undirected* graph from these data. 

<div id="solution">
Solution Here
</div>


c. Using the *directed* graph, calculate the alpha centrality using $s=\mathbf{1}_n$, the vector of all ones. Use $\alpha \in \{.1, .8\}$. 
For each $\alpha$, plot the results using color to distinguish between the fraud, non-fraud, and unknown nodes. Comment on what this tells you about the two unknown nodes. 

<div id="solution">
Solution Here
</div>


d. Repeat for the *undirected* graph using only $\alpha=.1$. 

<div id="solution">
Solution Here
</div>


e. Why can $\alpha=.8$ not be used for the *undirected* graph? What is the maximum value of $\alpha$ in this case? 

<div id="solution">
Solution Here
</div>



f. Using the *directed graph*, set $e=1$ for the known fraudsters, $e=0$ for the legitimate, and $e=.01$ for the unknown nodes. You can think of $e$ as proportional to the prior probability that a node is a fraudster. Calculate the alpha centrality (using $\alpha = .8$) and make the plot. Comment on what this tells you about the two unknown nodes. 


<div id="solution">
Solution Here
</div>





### Problem 2.3: Hubs and Authorities (HITS) 

**This problem is for graduate students. Undergrads do not need to complete**.

The HITS algorithm is described in [MMDS 5.5](http://infolab.stanford.edu/~ullman/mmds/ch5.pdf)


a. The HITS scores are designed to work with *directed* networks. What is the result of running HITS on an *undirected* network? Show that the scores reduce to a familiar centrality score. 

<div id="solution">
Solution Here
</div>



b. Write a function to calculate the Hubs and Authority scores. See MMDS 5.5.2 for details. 

<div id="solution">
Solution Here
</div>

c. Use your function to calculate the hubs and authority scores for the Political Blog data [Adamic and Glance (2005). "The political blogosphere and the 2004 U.S. election: divided they blog", In Proceedings of the *3rd International Workshop on Link discovery (LinkKDD '05)*. ACM, New York, NY, USA](https://github.com/mdporter/SYS6018/raw/master/other/(Adamic)%20Political%20Blogs.pdf).

- nodes: <https://raw.githubusercontent.com/mdporter/SYS6018/master/data/polblogs_nodes.csv>

- edges: <https://raw.githubusercontent.com/mdporter/SYS6018/master/data/polblogs.csv>

The `nodes` data has a column named `leaning` which indicates the political leaning (liberal or conservative) of the blog and a column named `label` which gives the blog name. 

Run HITS on the full data, and then report the top 5 hubs and top 5 authority scores (with blog name) for both liberal and conservative blogs.

- In the case of a failure in part b, use an existing functions, e.g. `hub.score()` and `authority.score()` from igraph.   
- Note: the network is *directed*
 

<div id="solution">
Solution Here
</div>











 


