---
title: "Homework #3"
author: "**Your Name Here**"
date: "Due: Thu Sept 17 | 1:55pm"
output: 
  html_document:
  # html_notebook:  
    df_print: default  # set default format for table output
editor_options: 
  chunk_output_type: console    
---


**SYS 6018 | Fall 2020 | University of Virginia **

*******************************************

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5,     # set figure width
                      fig.align = "center",# set figure position
                      out.width = "49%", # set width of displayed images
                      warning=FALSE,     # do not show R warnings
                      message=FALSE)     # do not show R messages
options(dplyr.summarise.inform = FALSE)  # ignore message about group structure

```

<!--- Solution Region --->
```{css solution-region, echo=FALSE}
.solution {
  background-color: #232D4B10;
  border-style: solid;
  border-color: #232D4B;
  padding: .5em;
  margin: 20px
}
```


<!--- Load Required R packages here --->
```{r packages, include=FALSE}
#- Better table printing
library(kableExtra) # https://haozhu233.github.io/kableExtra/awesome_table_in_html.html
format_table <- function(x, nmax=10) {
  kable(x) %>% 
    kable_styling(full_width = FALSE, font_size=11, position = "left") %>% 
    {if(nrow(x) > nmax) scroll_box(., width = "100%", height = "200px") else .}
}
#- useful functions
digits <- function(x, k=2) format(round(x, k), nsmall=k)
#- data directory
data.dir = 'https://mdporter.github.io/SYS6018/data/'
#- required functions
library(tidyverse)
library(glmnet)
```



### Problem 3.1: Optimal Tuning Parameters

In cross-validation, we discussed choosing the tuning parameter values that minimized the cross-validation error. Another approach, called the "one-standard error" rule [ISL pg 214, ESL pg 61], uses the values corresponding to the least complex model whose cv error is within one standard error of the best model. The goal of this assignment is to compare these two rules.

Use simulated data from `mlbench.friedman1(., sd=2)` in the `mlbench` R package and fit *lasso models*. The tuning parameter $\lambda$ (corresponding to the penalty on the coefficient magnitude) is the one we will focus one. Generate training data, use k-fold cross-validation to get $\lambda_{\rm min}$ and $\lambda_{\rm 1SE}$, generate test data, make predictions for the test data, and compare performance of the two rules under a squared error loss using a hypothesis test.  

Choose reasonable values for:

- Number of cv folds ($K$) 
    - Note: you are free to use repeated CV, repeated hold-outs, or bootstrapping instead of plain cross-validation; just be sure to describe what do did so it will be easier to grade.
- Number of training and test observations
- Number of simulations
- If everyone uses different values, we will be able to see how the results change over the different settings.
- Don't forget to make your results reproducible (e.g., set seed)

This pseudo code will get you started:
```yaml
library(mlbench)
library(glmnet)

#-- Settings
n.train =        # number of training obs
n.test =         # number of test obs
K =              # number of CV folds
alpha =          # glmnet tuning alpha (1 = lasso, 0 = ridge)
M =              # number of simulations

#-- Data Generating Function
getData <- function(n) mlbench.friedman1(n, sd=2) # data generating function

#-- Simulations
# Set Seed Here

for(m in 1:M) {

# 1. Generate Training Data
# 2. Build Training Model using cross-validation, e.g., cv.glmnet()
# 3. get lambda that minimizes cv error and 1 SE rule
# 4. Generate Test Data
# 5. Predict y values for test data (for each model)
# 6. Evaluate predictions

}

#-- Compare
# compare performance of the approaches / Statistical Test
```


a. Code for the simulation and performance results


<div class="solution">

Add your solutions here

</div>



b. Description and results of a hypothesis test comparing $\lambda_{\rm min}$ and $\lambda_{\rm 1SE}$.


<div class="solution">

Add your solutions here

</div>




<!--
------------------------------------------------------------------------------
Applied: ridge regression, tuning parameter optimization, GCV and LOOCV based selection, model.matrix() to deal with categorical
-->

### Problem 3.2 Prediction Contest: Real Estate Pricing


This problem uses the [realestate-train](https://mdporter.github.io/SYS6018/data/realestate-train.csv) and [realestate-test](https://mdporter.github.io/SYS6018/data/realestate-test.csv) (click on links for data). 

The goal of this contest is to predict sale price (in thousands) (`price` column) using an *elastic net* model. Evaluation of the test data will be based on the root mean squared error ${\rm RMSE}= \sqrt{\frac{1}{m}\sum_i (y_i - \hat{y}_i)^2}$ for the $m$ test set observations. 


a. Use an *elastic net* model to predict the `price` of the test data. Submit a .csv file (ensure comma separated format) named `lastname_firstname.csv` that includes the column named *yhat* that is your estimates. We will use automated evaluation, so the format must be exact. 
    - You are free to use any tuning parameters
    - You are free to use any data transformation or feature engineering
    - You will receive credit for a proper submission; the top five scores will receive 2 bonus points.     
    
<div class="solution">

Submit file to Collab

</div>    
    
    
b. Show the code you used to transform the data. Note: there are some categorical predictors so at the least you will have to convert those to something numeric (e.g., one-hot or dummy coding). 

<div class="solution">

Add your solutions here

</div>



c. Report the $\alpha$ and $\lambda$ parameters you used to make your final predictions. Describe how you choose those tuning parameters and show supporting code. 



<div class="solution">

Add your solutions here

</div>



d. Report the anticipated performance of your method in terms of RMSE. We will see how close your performance assessment matches the actual value. 

<div class="solution">

Add your solutions here

</div>





