---
title: "Homework #4"
author: "**Your Name Here**"
date: "Due: Thu Sept 24 | 1:55pm"
output: 
  html_document:
  # html_notebook:  
    df_print: default  # set default format for table output
---

**SYS 6018 | Fall 2020 | University of Virginia **

*******************************************

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5,     # set figure width
                      fig.align = "center",# set figure position
                      out.width = "49%", # set width of displayed images
                      warning=FALSE,     # do not show R warnings
                      message=FALSE)     # do not show R messages
options(dplyr.summarise.inform = FALSE)  # ignore message about group structure
```

<!--- Solution Region --->
```{css solution-region, echo=FALSE}
.solution {
  background-color: #232D4B10;
  border-style: solid;
  border-color: #232D4B;
  padding: .5em;
  margin: 20px
}
```


<!--- Load Required R packages here --->
```{r formatting, include=FALSE}
#- Better table printing
library(kableExtra) # https://haozhu233.github.io/kableExtra/awesome_table_in_html.html
format_table <- function(x, nmax=10) {
  kable(x) %>% 
    kable_styling(full_width = FALSE, font_size=11, position = "left") %>% 
    {if(nrow(x) > nmax) scroll_box(., width = "100%", height = "200px") else .}
}
#- useful functions
digits <- function(x, k=2) format(round(x, k), nsmall=k)
#- data directory
data.dir = 'https://mdporter.github.io/SYS6018/data/'
#- required functions
library(tidyverse)
library(glmnet)
```



## Crime Linkage

Crime linkage attempts to determine if two or more unsolved crimes share a common offender. *Pairwise* crime linkage is the more simple task of deciding if two crimes share a common offender; it can be considered a binary classification problem. The linkage training data has 8 evidence variables that measure the similarity between a pair of crimes:

- `spatial` is the spatial distance between the crimes
- `temporal` is the fractional time (in days) between the crimes
- `tod` and `dow` are the differences in time of day and day of week between the crimes
- `LOC`, `POA,` and `MOA` are binary with a 1 corresponding to a match (type of property, point of entry, method of entry)
- `TIMERANGE` is the time between the earliest and latest possible times the crime could have occurred (because the victim was away from the house during the crime).
- The response variable indicates if the crimes are linked ($y=1$) or unlinked ($y=0$).


These problems use the [linkage-train](https://mdporter.github.io/SYS6018/data/linkage_train.csv) and [linkage-test](https://mdporter.github.io/SYS6018/data/linkage_test.csv) datasets (click on links for data). 


### Problem 4.1: Penalized Regression for Crime Linkage

a. Fit a penalized *linear regression* model. Use a lasso, ridge, or elasticnet penalty (your choice). 
    - Report the value of $\alpha$ used (if elasticnet)
    - Report the value of $\lambda$ used
    - Report the estimated coefficients


<div class="solution"> 

Add Solution Here

</div>


b. Fit a penalized *logistic regression* model. Use a lasso, ridge, or elasticnet penalty (your choice).  
    - Report the value of $\alpha$ used (if elasticnet)
    - Report the value of $\lambda$ used
    - Report the estimated coefficients

<div class="solution"> 

Add Solution Here

</div>

c. Produce one plot that has the ROC curves, using the *training data*, for both models (from part a and b). Use color and/or linetype to distinguish between models and include a legend.    

<div class="solution"> 

Add Solution Here

</div>


d. Recreate the ROC curve from the penalized logistic regression model using repeated hold-out data. The following steps will guide you:
    - Fix $\alpha=.75$ 
    - Run the following steps 25 times:
    i. Hold out 500 observations
    ii. Use the remaining observations to estimate $\lambda$ 
    iii. Predict the probability of the 500 hold-out observations
    iv. Store the predictions and hold-out labels
    - Combine the results and produce the hold-out based ROC curve
    - Note: by estimating $\lambda$ each iteration, we are incorporating the uncertainty present in estimating that tuning parameter. 
    
<div class="solution"> 

Add Solution Here

</div>


e. Contest Part 1: Predict the estimated *probability* of linkage for the test data (using any model). 
    - Submit a .csv file (ensure comma separated format) named `lastname_firstname_1.csv` that includes the column named **p** that is your estimated posterior probability. We will use automated evaluation, so the format must be exact. 
    - You are free to use any tuning parameters
    - You are free to use any data transformation or feature engineering
    - You will receive credit for a proper submission; the top five scores will receive 2 bonus points.     
    - Your probabilities will be evaluated with respect to the mean negative Bernoulli log-likelihood (known as the average *log-loss* metric)
$$ 
L = - \frac{1}{M} \sum_{i=1}^m [y_i \log \, \hat{p}_i + (1 - y_i) \log \, (1 - \hat{p}_i)]
$$
where $M$ is the number of test observations, $\hat{p}_i$ is the prediction for the $i$th test observation, and $y_i \in \{0,1\}$ are the true test set labels. 

<div class="solution"> 

Show code here

</div>


f. Contest Part 2: Predict the linkages for the test data (using any model). 
    - Submit a .csv file (ensure comma separated format) named `lastname_firstname_2.csv` that includes the column named **link** that takes the value of 1 for linkages and 0 for unlinked pairs. We will use automated evaluation, so the format must be exact. 
    - You are free to use any tuning parameters.
    - You are free to use any data transformation or feature engineering.
    - Your labels will be evaluated based on total cost, where cost is equal to `1*FP + 8*FN`. This implies that False Negatives (FN) are 8 times as costly as False Negatives (FP)    
    - You will receive credit for a proper submission; the top five scores will receive 2 bonus points. Note: you only will get bonus credit for one of the two contests. 

<div class="solution"> 

Show code here

</div>






