---
title: "Homework #4: Classification" 
author: "**Your Name Here**"
date: "Due: Wed Mar 01 | 11:45am"
output: R6018::homework
---

**SYS 4582/6018 | Spring 2023 | University of Virginia **

*******************************************
```{r config, echo=FALSE}
source(system.file("config/hw_config.R", package="R6018")) # knitr settings
# options(dplyr.summarise.inform = FALSE)  # ignore dplyr message about grouping
```

::: {style="background-color:yellow; color:red; display: block; border-color: black; padding:1em"}
This is an **independent assignment**. Do not discuss or work with classmates.
:::


# Required R packages and Directories

::: {.solution}
```{r packages, message=FALSE, warning=FALSE}
data.dir = 'https://mdporter.github.io/SYS6018/data/' # data directory
library(glmnet)    # for glmnet() functions
library(yardstick) # for evaluation metrics
library(R6018)     # functions for SYS-6018
library(tidyverse) # functions for data manipulation   
```
:::


# Crime Linkage

Crime linkage attempts to determine if two or more unsolved crimes share a common offender. *Pairwise* crime linkage is the more simple task of deciding if two crimes share a common offender; it can be considered a binary classification problem. The linkage training data has 8 evidence variables that measure the similarity between a pair of crimes:

- `spatial` is the spatial distance between the crimes
- `temporal` is the fractional time (in days) between the crimes
- `tod` and `dow` are the differences in time of day and day of week between the crimes
- `LOC`, `POA,` and `MOA` are binary with a 1 corresponding to a match (type of property, point of entry, method of entry)
- `TIMERANGE` is the time between the earliest and latest possible times the crime could have occurred (because the victim was away from the house during the crime).
- The response variable indicates if the crimes are linked ($y=1$) or unlinked ($y=0$).


These problems use the [linkage-train](https://mdporter.github.io/SYS6018/data/linkage_train.csv) and [linkage-test](https://mdporter.github.io/SYS6018/data/linkage_test.csv) datasets (click on links for data). Load the data here:



::: {.solution}
Add Solution Here
:::




# Problem 1: Penalized Regression for Crime Linkage

## a. Penalized linear regression 

Fit a penalized *linear* regression model to predict linkage. Use a lasso, ridge, or elasticnet penalty (your choice). 

- Report the value of $\alpha$ used (if elasticnet)
- Report the value of $\lambda$ used
- Report the estimated coefficients

::: {.solution}
Add Solution Here
:::


## b. Penalized logistic regression

Fit a penalized *logistic* regression model to predict linkage. Use a lasso, ridge, or elasticnet penalty (your choice).  

- Report the value of $\alpha$ used (if elasticnet)
- Report the value of $\lambda$ used
- Report the estimated coefficients

::: {.solution}
Add Solution Here
:::


## c. ROC Curves (training data)

Produce one plot that has the ROC curves, using the *training data*, for both models (from part a and b). Use color and/or linetype to distinguish between models and include a legend.   

::: {.solution}
Add Solution Here
:::


## d. ROC Curve (hold-out data)

Recreate the ROC curve from the penalized logistic regression model using repeated hold-out data. The following steps will guide you:

- Fix $\alpha=.75$ 
- Run the following steps 25 times:
i. Hold out 500 observations
ii. Use the remaining observations to estimate $\lambda$ using 10-fold CV
iii. Predict the probability of linkage for the 500 hold-out observations
iv. Store the predictions and hold-out labels
- Combine the results and produce the hold-out based ROC curve
- Note: by estimating $\lambda$ each iteration, we are incorporating the uncertainty present in estimating that tuning parameter. 
    
::: {.solution}
Add Solution Here
:::


## e. Contest Part 1: Probability

Predict the estimated *probability* of linkage for the test data (using any model). 

- Submit a .csv file (ensure comma separated format) named `lastname_firstname_1.csv` that includes the column named **p** that is your estimated posterior probability. We will use automated evaluation, so the format must be exact. 
- You are free to use any tuning parameters
- You are free to use any data transformation or feature engineering
- You will receive credit for a proper submission; the top five scores will receive 2 bonus points.     
- Your probabilities will be evaluated with respect to the mean negative Bernoulli log-likelihood (known as the average *log-loss* metric)
$$ 
L = - \frac{1}{M} \sum_{i=1}^m [y_i \log \, \hat{p}_i + (1 - y_i) \log \, (1 - \hat{p}_i)]
$$
where $M$ is the number of test observations, $\hat{p}_i$ is the prediction for the $i$th test observation, and $y_i \in \{0,1\}$ are the true test set labels. 

::: {.solution}
Add Solution Here
:::


## f. Contest Part 2: Linkages

Predict the linkages for the test data (using any model). 

- Submit a .csv file (ensure comma separated format) named `lastname_firstname_2.csv` that includes the column named **linkage** that takes the value of 1 for linkages and 0 for unlinked pairs. We will use automated evaluation, so the format must be exact. 
- You are free to use any tuning parameters.
- You are free to use any data transformation or feature engineering.
- Your labels will be evaluated based on total cost, where cost is equal to `1*FP + 8*FN`. This implies that False Negatives (FN) are 8 times as costly as False Positives (FP)    
- You will receive credit for a proper submission; the top five scores will receive 2 bonus points. Note: you only will get bonus credit for one of the two contests. 


::: {.solution}
Add Solution Here
:::






