---
title: "Homework #5: Density Estimation" 
author: "**Your Name Here**"
date: "Due: Tue Mar 22 | 10:30 am"
output: R6018::homework
editor_options:
  chunk_output_type: console
---

**SYS 4582/6018 | Spring 2022 | University of Virginia **

*******************************************
```{r config, echo=FALSE}
source(system.file("config/hw_config.R", package="R6018")) # knitr settings
options(dplyr.summarise.inform = FALSE)  # ignore dplyr message about grouping
```


# Required R packages and Directories

::: {.solution}
```{r packages, message=FALSE, warning=FALSE}
data.dir = 'https://mdporter.github.io/SYS6018/data/' # data directory
library(R6018)     # functions for SYS 6018
library(ks)        # functions for KDE
library(tidyverse) # functions for data manipulation   
```
:::



# Problem 1 Geographic Profiling

Geographic profiling, a method developed in criminology, can be used to estimate the [home location (roost) of animals](https://www.sciencedirect.com/science/article/pii/S0022519305004157) based on a collection of sightings. The approach requires an estimate of the distribution the animal will travel from their roost to forage for food. 

A sample of $283$ distances that pipistrelle bats traveled (in meters) from their roost can be found at: 

- **Bat Data**: <`r file.path(data.dir, 'geo_profile.csv')`>

One probability model for the distance these bats will travel is:
\begin{align*}
f(x; \theta) = \frac{x}{\theta} \exp \left( - \frac{x^2}{2 \theta} \right)
\end{align*}
where the parameter $\theta > 0$ controls how far they are willing to travel. 


## a. Derive the MLE for $\theta$ (i.e., show the math). 

::: {.solution}
Add solution here
:::


## b. What is the MLE of $\theta$ for the bat data? (Use results from a, or use computational methods.) 

::: {.solution}
Add solution here
:::

## c. Using the MLE value of $\theta$ from part b, compute the estimated density at a set of evaluation points between 0 and 8 meters. Plot the estimated density.

::: {.solution}
Add solution here
:::

## d. Estimate the density using KDE. Report the bandwidth you chose and produce a plot of the estimated density. 

::: {.solution}
Add solution here
:::




## e. Which model do you prefer, the parametric or KDE? 

::: {.solution}
Add solution here
:::




# Problem 2: Interstate Crash Density

Interstate 64 (I-64) is a major east-west road that passes just south of Charlottesville. Where and when are the most dangerous places/times to be on I-64? The crash data (link below) gives the mile marker and fractional time-of-week for crashes that occurred on I-64 between mile marker 87 and 136 in 2016. The time-of-week data takes a numeric value of *\<dow\>.\<hour/24\>*, where the dow starts at 0 for Sunday (6 for Sat) and the decimal gives the time of day information. Thus `time=0.0417` corresponds to Sun at 1am and `time=6.5` corresponds to Sat at noon. 

- **Crash Data**: <`r file.path(data.dir, 'crashes16.csv')`>


## a. Extract the crashes and make a scatter plot with mile marker on x-axis and time on y-axis. 

::: {.solution}
Add solution here
:::



## b. Use KDE to estimate the *mile marker* density. 

- Report the bandwidth. 
- Plot the density estimate.

::: {.solution}
Add solution here
:::

## c. Use KDE to estimate the temporal *time-of-week* density. 

- Report the bandwidth. 
- Plot the density estimate. 

::: {.solution}
Add solution here
:::

## d. Use KDE to estimate the bivariate mile-time density. 

- Report the bandwidth parameters.
- Plot the bivariate density estimate. 

::: {.solution}
Add solution here
:::


## e. Based on the estimated density, approximate the most dangerous place and time to drive on this strech of road. Identify the mile marker and time-of-week pair. 

::: {.solution}
Add solution here
:::


		