---
title: "Homework #5"
author: "**Your Name Here**"
date: "Due: Thu Oct 8 | 1:55pm"
output: 
  html_document:
  # html_notebook:  
    df_print: default  # set default format for table output
---

**SYS 6018 | Fall 2020 | University of Virginia **

*******************************************

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5,     # set figure width
                      fig.align = "center",# set figure position
                      out.width = "49%", # set width of displayed images
                      warning=TRUE,      # show R warnings
                      message=TRUE)      # show R messages
options(dplyr.summarise.inform = FALSE)  # ignore message about group structure
```

<!--- Solution Region --->
```{css solution-region, echo=FALSE}
.solution {
  background-color: #232D4B10;
  border-style: solid;
  border-color: #232D4B;
  padding: .5em;
  margin: 20px
}
```


<!--- Load Required R packages here --->
```{r packages, include=FALSE}
#- Better table printing
library(kableExtra) # https://haozhu233.github.io/kableExtra/awesome_table_in_html.html
format_table <- function(x, nmax=10) {
  kable(x) %>% 
    kable_styling(full_width = FALSE, font_size=11, position = "left") %>% 
    {if(nrow(x) > nmax) scroll_box(., width = "100%", height = "200px") else .}
}
#- useful functions
digits <- function(x, k=2) format(round(x, k), nsmall=k)
#- data directory
data.dir = 'https://mdporter.github.io/SYS6018/data/'
#- required functions
library(tidyverse)
library(glmnet)
```




### Problem 5.1 Geographic Profiling

```{r, echo=FALSE, eval=FALSE}
set.seed(2019)
n = 283
sd = 2.1
x = sqrt(rnorm(n, sd=sd)^2 + rnorm(n, sd=sd)^2)

readr::write_csv(tibble(x), "../data/geo_profile.csv", col_names=FALSE)
#hist(x, 15)

```

Geographic profiling, a method developed in criminology, can be used to estimate the [home location (roost) of animals](https://www.sciencedirect.com/science/article/pii/S0022519305004157) based on a collection of sightings. The approach requires an estimate of the distribution the animal will travel from their roost to forage for food. 

A sample of $283$ distances that pipistrelle bats traveled (in meters) from their roost can be found at: 
<https://mdporter.github.io/SYS6018/data/geo_profile.csv>


One probability model for the distance these bats will travel is:
\begin{align*}
f(x; \theta) = \frac{x}{\theta} \exp \left( - \frac{x^2}{2 \theta} \right)
\end{align*}
where the parameter $\theta > 0$ controls how far they are willing to travel. 


a. Derive the MLE for $\theta$ (i.e., show the math). 

<div class="solution"> 

</div>



b. What is the MLE of $\theta$ for the bat data? (Use results from a, or use computational methods.) 

<div class="solution"> 

</div>



c. Using the MLE value of $\theta$ from part b, compute the estimated density of this distribution at a set of evaluation points between 0 and 8 meters. Plot the estimated density.

<div class="solution"> 

</div>



d. Estimate the density using KDE. Report the bandwidth you chose and produce a plot of the estimated density. 


<div class="solution"> 

</div>



e. Which model do you prefer, the parametric or KDE? 

<div class="solution"> 

</div>





### Problem 5.2: Interstate Crash Density

Interstate 64 (I-64) is a major east-west road that passes just south of Charlottesville. Where and when are the most dangerous places/times to be on I-64? The crash data (link below) gives the mile marker and fractional time-of-week for crashes that occurred on I-64 between mile marker 87 and 136 in 2016. The time-of-week data takes a numeric value of *\<dow\>.\<hour/24\>*, where the dow starts at 0 for Sunday (6 for Sat) and the decimal gives the time of day information. Thus `time=0.0417` corresponds to Sun at 1am and `time=6.5` corresponds to Sat at noon). 

- **Crash Data**: <https://mdporter.github.io/SYS6018/data/crashes16.csv>


a. Extract the crashes and make a scatter plot with mile marker on x-axis and time on y-axis. 


<div class="solution"> 

</div>



b. Use KDE to estimate the *mile marker* density. Report the bandwidth and plot the density estimate. 

<div class="solution"> 

</div>


c. Use KDE to estimate the temporal *time-of-week* density. Report the bandwidth and plot the density estimate. 

<div class="solution"> 

</div>



d. Use KDE to estimate the bivariate mile-time density. What are the bandwidth parameters? Plot the bivariate density estimate. 


<div class="solution"> 

</div>


e. Based on the estimated density, approximate the most dangerous mile marker and time-of-week. 

<div class="solution"> 

</div>

