---
title: "Homework #6"
author: "**Your Name Here**"
date: "Due: Mon Oct 21 2:00pm"
output: html_document
---

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5,     # set figure width
                      fig.align = "center",# set figure position
                      out.width = "49%", # set width of displayed images
                      warning=FALSE,     # do not show R warnings
                      message=FALSE)     # do not show R messages
```

<!--- Solution Region --->
<style>
#solution {
  background-color: #8FBC8F;
  border-style: solid;
  border-color: blue;
  padding: .5em;
  margin: 20px
}
</style>



**SYS 6018 | Fall 2019 | University of Virginia **

*******************************************

<!--- Load Required R packages here --->
```{r, include=FALSE}
library(tidyverse)
digits <- function(x, k=2) format(round(x, k), nsmall=k)
data.dir = 'https://raw.githubusercontent.com/mdporter/SYS6018/master/data'
```





### Problem 6.1: Evaluating a Regression Model

a. Create a set of functions to generate data from the following distributions:
\begin{align*}
X &\sim \mathcal{N}(0, 1) \\
Y &= -1 + .5X + .2X^2 + \epsilon \\
\epsilon &\sim \mathcal{N}(0,\, \sigma)
\end{align*}

<div id="solution">
SOLUTION HERE
</div>




b. Simulate $n=100$ realizations from these distributions using $\sigma=3$. Produce a scatterplot and draw the true regression line $f(x) = E[Y \mid X=x]$. Use `set.seed(611)` prior to generating the data.

<div id="solution">
SOLUTION HERE
</div>


c. Fit three polynomial regression models using least squares: linear, quadratic, and cubic. Produce another scatterplot, add the fitted lines and true population line $f(x)$  using different colors, and add a legend that maps the line color to a model.
    - Note: Notice that while the true model is quadratic, we are also fitting linear (less complex) and cubic (more complex) models. 

<div id="solution">
SOLUTION HERE
</div>


d. Simulate a test data set of $10000$ observations from the same distributions. Use `set.seed(612)` prior to generating the test data. Calculate the estimated mean squared error (MSE) for each model.
Are the results as expected? 


<div id="solution">
SOLUTION HERE
</div>



e. What is the best achievable MSE? That is, what is the MSE if the true $f(x)$ was used to evaluate the test set? How close does the best method come to achieving the optimum? 


<div id="solution">
SOLUTION HERE
</div>


f. The MSE scores obtained in part *d* came from one realization of training data. Here will we explore how much variation there is in the MSE scores by replicating the simulation many times. 
    - Re-run the same simulation in part *d* 100 times. 
    - Create kernel density plots (you choose bandwidth) of the resulting MSE values for each model. 
    - Use `set.seed(613)` prior to running the simulation and do not set the seed in any other places.


<div id="solution">
SOLUTION HERE
</div>


g. Show a count of how many times each model was the best. That is, out of the 100 simulations, count how many times each model had the lowest MSE.

<div id="solution">
SOLUTION HERE
</div>



h. Repeat the simulation in part *g*, but use $\sigma=2$. Report the number of times each model was best (you do not need to produce any plots). Use the same `set.seed(613)` prior to running the simulation and do not set the seed in any other places.

<div id="solution">
SOLUTION HERE
</div>



i. Repeat *g*, but now use $\sigma=4$ and $n=200$. 

<div id="solution">
SOLUTION HERE
</div>


j. Describe the effects $\sigma$ and $n$ has on selection of the best model? Why is the *true* model form (i.e., quadratic) not always the *best* model to use when prediction is the goal? 

<div id="solution">
SOLUTION HERE
</div>


