---
title: "Homework #8: Clustering" 
author: "**Your Name Here**"
date: "Due: Tue Apr 26 | 10:30am"
output: R6018::homework
---

**SYS 4582/6018 | Spring 2022 | University of Virginia **

*******************************************
```{r config, echo=FALSE}
source(system.file("config/hw_config.R", package="R6018")) # knitr settings
# options(dplyr.summarise.inform = FALSE)  # ignore dplyr message about grouping
```


# Required R packages and Directories

::: {.solution}
```{r packages, message=FALSE, warning=FALSE}
data.dir = 'https://mdporter.github.io/SYS6018/data/' # data directory
library(R6018)     # functions for SYS-6018
library(tidyverse) # functions for data manipulation   
library(mclust)    # functions for mixture models
library(mixtools)  # poisregmixEM() function
```
:::


# Problem 1: Customer Segmentation with RFM (Recency, Frequency, and Monetary Value)

RFM analysis is an approach that some businesses use to understand their customers' activities. At any point in time, a company can measure how recently a customer purchased a product (Recency), how many times they purchased a product (Frequency), and how much they have spent (Monetary Value). There are many ad-hoc attempts to segment/cluster customers based on the RFM scores (e.g., here is one based on using the customers' rank of each dimension independently: <https://joaocorreia.io/blog/rfm-analysis-increase-sales-by-segmenting-your-customers.html>). In this problem you will use the clustering methods we covered in class to segment the customers. 


The data for this problem can be found here: <`r file.path(data.dir, "RFM.csv")`>. Cluster based on the Recency, Frequency, and Monetary value columns.


::: {.solution}
Load Data
:::

## a. Implement hierarchical clustering. 

- Describe any pre-processing steps you took (e.g., scaling, distance metric)
- State the linkage method you used with justification. 
- Show the resulting dendrogram
- State the number of segments/clusters you used with justification. 
- Using your segmentation, are customers 1 and 100 in the same cluster?     
    
::: {.solution}
Add Solution here
:::


## b. Implement k-means.  

- Describe any pre-processing steps you took (e.g., scaling)
- State the number of segments/clusters you used with justification. 
- Using your segmentation, are customers 1 and 100 in the same cluster?     
    
::: {.solution}
Add Solution here
:::

## c. Implement model-based clustering

- Describe any pre-processing steps you took (e.g., scaling)
- State the number of segments/clusters you used with justification. 
- Describe the best model. What restrictions are on the shape of the components?
- Using your segmentation, are customers 1 and 100 in the same cluster?     


::: {.solution}
Add Solution here
:::

## d. Discuss how you would cluster the customers if you had to do this for your job. Do you think one model would do better than the others? 

::: {.solution}
Add Solution here
:::



# Problem 2: Poisson Mixture Model (OPTIONAL: NOT GRADED)

The pmf of a Poisson random variable is:
\begin{align*}
f_k(x; \lambda_k) = \frac{\lambda_k^x e^{-\lambda_k}}{x!}
\end{align*}

A two-component Poisson mixture model can be written:
\begin{align*}
f(x; \theta) = \pi \frac{\lambda_1^x e^{-\lambda_1}}{x!} + (1-\pi) \frac{\lambda_2^x e^{-\lambda_2}}{x!}
\end{align*}



## a. What are the parameters of the model? 

::: {.solution}
Add Solution here
:::

## b. Write down the log-likelihood for $n$ independent observations ($x_1, x_2, \ldots, x_n$). 

::: {.solution}
Add Solution here
:::

## c. Suppose we have initial values of the parameters. Write down the equation for updating the *responsibilities*. 

::: {.solution} 
Add Solution here
:::


## d. Suppose we have responsibilities, $r_{ik}$ for all $i=1, 2, \ldots, n$ and $k=1,2$. Write down the equations for updating the parameters. 

::: {.solution}
Add Solution here
:::


## e. Fit a two-component Poisson mixture model, report the estimated parameter values, and show a plot of the estimated mixture pmf for the following data:

```{r, echo=TRUE}
#-- Run this code to generate the data
set.seed(123)             # set seed for reproducibility
n = 200                   # sample size
z = sample(1:2, size=n, replace=TRUE, prob=c(.25, .75)) # sample the latent class
theta = c(8, 16)          # true parameters
y = ifelse(z==1, rpois(n, lambda=theta[1]), rpois(n, lambda=theta[2]))
```


<div style="background-color:lightgrey; display: block; border-color: black; padding:1em">

Note: The function `poisregmixEM()` in the R package `mixtools` is designed to estimate a mixture of *Poisson regression* models. We can still use this function for our problem of density estimation if it is recast as an intercept-only regression. To do so, set the $x$ argument (predictors) to `x = rep(1, length(y))` and `addintercept = FALSE`. 

Look carefully at the output from this model. The `beta` values (regression coefficients) are on the log scale.

</div>

::: {.solution}
Add Solution here
:::

## f. **2 pts Extra Credit**: Write a function that estimates this two-component Poisson mixture model using the EM approach. Show that it gives the same result as part *e*. 
- Note: you are not permitted to copy code.  Write everything from scratch and use comments to indicate how the code works (e.g., the E-step, M-step, initialization strategy, and convergence should be clear). 
- Cite any resources you consulted to help with the coding. 


::: {.solution}
Add Solution here
:::


