---
title: "Homework #8"
author: "**Your Name Here**"
date: "Due: Mon Apr 1 9:30am"
output: html_document
---

<!--- Below are global settings for knitr. You can override any of them by adding the changes to individual chunks --->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      cache=FALSE,       # don't cache anythin by default
                      collapse=FALSE,    # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 5,     # set figure width
                      out.width = "50%", # set width of displayed images
                      warning=FALSE,     # do not show R warnings
                      message=FALSE)     # do not show R messages
```

<!--- Solution Region --->
<style>
#solution {
  background-color: #8FBC8F;
  border-style: solid;
  border-color: blue;
  padding: .5em;
  margin: 20px
}
</style>



**SYS 4582/6018 | Spring 2019 | University of Virginia **

*******************************************

<!--- Load Required R packages here --->
```{r, include=FALSE}
library(tidyverse)
digits <- function(x, k=2) format(round(x, k), nsmall=k)
data.dir = 'https://raw.githubusercontent.com/mdporter/SYS6018/master/data'
```



### Problem 8.1: Optimal Tuning Parameters

In cross-validation, we discussed choosing the tuning parameter values that minimized the cross-validation error. Another approach, called the "one-standard error" rule [ISL pg 214, ESL pg 61], uses the values corresponding to the least complex model whose cv error is within one standard error of the best model. The goal of this assignment is to compare these two rules.

Use simulated data from `mlbench.friedman1(., sd=2)` in the `mlbench` R package and fit *lasso models*. The tuning parameter $\lambda$ (corresponding to the penalty on the coefficient magnitude) is the one we will focus one. Generate training data, use k-fold cross-validation to get $\lambda_{\rm min}$ and $\lambda_{\rm 1SE}$, generate test data, make predictions for the test data, and compare performance of the two rules using mean squared error using a hypothesis test.    

Choose reasonable values for:

- Number of cv folds ($K$)
- Number of training and test observations
- Number of simulations
- If everyone uses different values, we will be able to see how the results change over the different settings.
- Don't forget to make your results reproducible (e.g., set seed)

This pseudo code will get you started:
```yaml
library(mlbench)
library(glmnet)

#-- Settings
n.train =        # number of training obs
n.test =         # number of test obs
K =              # number of CV folds
alpha =          # glmnet tuning alpha (1 = lasso, 0 = ridge)
M =              # number of simulations

#-- Data Generating Function
getData <- function(n) mlbench.friedman1(n, sd=2) # data generating function

#-- Simulations

for(m in 1:M){

# 1. Generate Training Data
# 2. Build Training Model using cross-validation, e.g., cv.glmnet()
# 3. get lambda that minimizes cv error and 1 SE rule
# 4. Generate Test Data
# 5. Predict y values for test data (for each model)
# 6. Evaluate predictions

}

#-- Compare
# compare performance of the approaches
```


<div id="solution">
SOLUTION HERE
</div>





### Problem 8.2 Prediction Contest: Real Estate Pricing


This problem uses the [realestate-train](https://mdporter.github.io/SYS6018/data/realestate-train.csv) and [realestate-test](https://mdporter.github.io/SYS6018/data/realestate-test.csv) (click on links for data). 

The goal of this contest is to predict sale price (in thousands) (`price` column) using an *elastic net* model. Evaluation of the test data will be based on the root mean squared error ${\rm RMSE}= \sqrt{\frac{1}{n}\sum_i (y_i - \hat{y}_i)^2}$ for the $n$ test set observations. 


a. Use an *elastic net* model to predict the `price` of the test data. Submit a .csv file (ensure comma separated format) named `lastname_firstname.csv` that includes the column named *yhat* that is your estimates. We will use automated evaluation, so the format must be exact. 
    - You are free to use any tuning parameters
    - You are free to use any data transformation or feature engineering
    - You will receive credit for a proper submission; the top five scores will receive 2 bonus points. 
    
<div id="solution">
SOLUTION HERE
</div>
    
    
b. Show the code you used to transform the data. Note: there are some categorical predictors so at the least you will have to convert those to something numeric (e.g., dummy coding). 

<div id="solution">
SOLUTION HERE
</div>



c. Report the $\alpha$ and $\lambda$ parameters you used to make your final predictions. Describe how you choose those tuning parameters and show supporting code. 

<div id="solution">
SOLUTION HERE
</div>



d. Report the anticipated performance of your method in terms of RMSE. We will see how close your performance assessment matches the actual value. 

<div id="solution">
SOLUTION HERE
</div>









