---
title: "Homework #9: Association Analysis" 
author: "**Your Name Here**"
date: "Due: Tue May 3 | 10:30 am"
output: R6018::homework
---

**SYS 4582/6018 | Spring 2022 | University of Virginia **

*******************************************
```{r config, echo=FALSE}
source(system.file("config/hw_config.R", package="R6018")) # knitr settings
# options(dplyr.summarise.inform = FALSE)  # ignore dplyr message about grouping
```


# Required R packages and Directories

::: {.solution}
```{r packages, message=FALSE, warning=FALSE}
data.dir = 'https://mdporter.github.io/SYS6018/data/' # data directory
library(R6018)     # functions for DS-6018
library(arules)    # functions for Association Rules
library(tidyverse) # functions for data manipulation
# Add others if necessary
```
:::



# Problem 1: Interestingness 

Suppose we have market basket data consisting of 100 transactions and 20 items. Assume the support for item {$a$} is 20%, support for item {$b$} is 85%, and support for itemset {$a,b$} is 15%. 


## a. What is the confidence of the rule {a} $\rightarrow$ {b}? 

::: {.solution}
Solution Here
:::


## b. Will the apriori algorithm find this rule (interesting) if the confidence threshold (minconf) is $c=.60$ and the support threshold (minsup) is $s=.10$?  

::: {.solution}
Solution Here
:::


## c. Find the *lift* of this rule. 

::: {.solution}
Solution Here
:::

## d. Find the *addedValue* of this rule. 

::: {.solution}
Solution Here
:::


## e. Find the *leverage/PS* of this rule. 

::: {.solution}
Solution Here
:::


## f. Describe the nature of the relationship between items {a} and {b} according to *lift*, *addedValue* and *leverage/PS*. What observation can you draw from parts (b) and (c-e)? 

::: {.solution}
Solution Here
:::

## g. Let $p(a)$, $p(b)$, and $p(a,b)$ be the actual probabilities of observing items {a}, {b}, and {a,b} respectively in a transaction. What is the expected confidence rule {a} $\rightarrow$ {b} if a and b are independent? 

::: {.solution}
Solution Here
:::



# Problem 2: Online Retail

The website <http://archive.ics.uci.edu/ml/datasets/online+retail> describes some transactional data from an online retailer. 


## a. Download the [excel file](http://archive.ics.uci.edu/ml/machine-learning-databases/00352/Online%20Retail.xlsx) to your machine and read it into R. 
- Loading Excel data: `readxl::read_excel()` (part of tidyverse)


::: {.solution}
Solution Here
:::


## b. There are many quality problems with this dataset, but we will only address two of them. Remove all of the rows with missing Description values (NAs) and remove any duplicate items in a single transaction. Print the first 10 rows of the resulting data. 

::: {.solution}
Solution Here
:::

## c. Find the number of transactions and number of items using *InvoiceNo* for transactions and *Description* as items (i.e., ignore the *StockCode* column).

::: {.solution}
Solution Here
:::


## d. Convert the data frame into a *transaction list* and convert it into a *transactions object* (don't forget to load the `arules` package). Print a summary (using `summary()`) of the new object. 

::: {.solution}
Solution Here
:::

## e. Find the items with the highest support. Print and plot the support of the top 10. 

::: {.solution}
Solution Here
:::

## f. Find the *frequent itemsets* that contain at least 3 items and have $s\geq 0.02$. Add the *lift* metric. Show all results, ordered by *lift*. 

::: {.solution}
Solution Here
:::

## g. Find all of the *association rules* with $s \geq 0.02$, $c \geq 0.70$. Add the *PS/leverage* and *addedValue* metrics. Show all results, ordered by *addedValue*

::: {.solution}
Solution Here
:::


## h. Find one rule that you think is interesting. Write the rule and explain why you find it interesting. 

::: {.solution}
Solution Here
:::

